The Freeplay Sandbox: a Novel Methodology for the Evaluation of Social Robotics

### 2017-10-06 paper.tex
Checking with Emmanuel what remains to be done

\section{Technical Implementation}
\label{sec:impl}

@@

\subsection{Supervisor}
A web interface can be used by the experimenter to manage the meta parameters of
the interaction: log data on the subjects, start-stop, select a task, manage data recording...

@@

\subsection{Records and logs}

Maybe redundant with Data  collection.

\subsection{Tools}

@@

@@

\subsection{RGB-D streams analysis}

@@

\subsection{Audio processing}

@@

\subsection{Game interactions analysis}

@@

>>>>

\section{Task Implementation}
\label{sec:impl}

@@

\todo{briefly present ROS pipeline for sensors}

@@

\subsection{Experiment Manager}

A web interface can be used by the experimenter to manage the meta parameters of
the interaction: log data on the subjects, start-stop, select a task, manage data recording...

@@

\subsection{Protocol}

\todo{TBD}

@@

\subsection{Data processing}

@@

\paragraph{Audio processing}

@@

\paragraph{Game interactions analysis}

\todo{check section title}

@@

\todo{Mention the annotator tool}
